rapr: Representative and Adequate Prioritisations in R

### 2016-06-16 code/rmarkdown/article.Rmd
+ article changes + increase threads

<!-- biodiversity processes are important -->
To fulfil the overarching aims of conservation, reserve networks must preserve both ecological and evolutionary processes [@r3; @r255]. Ecological processes, such as predator-prey interactions, pollination, and decomposition, are required for biodiversity to persist over short time-scales. Typically, they operate over small geographic domains--with exceptions such as migration and refugial habitats--and can be preserved using suitably large planning units [@r446] that each contain a discrete unit of habitat [@r448]. On the other hand, evolutionary processes are required for biodiversity to persist over long time-scales, and they typically operate over large geographic domains. Protected areas must preserve adaptive evolutionary processes to foster resilience against environmental change [eg. climate change; @r247]. Protected areas must also preserve neutral evolutionary processes [@r5; @r67; @r63]. These processes are associated with the breakdown of gene flow between populations. They are important for maintaining genetic diversity, and avoiding inbreeding depression. In recent decades, a wealth of data on biodiversity processes has become available to conservation planners [eg. bioclimatic, genetic, and trait data; @r33; @r453; @481]. Yet this data is only rarely used to guide conservation planning [@r61]. This is due to that fact that existing reserve selection tools focus on preserving biodiversity patterns or processes--but not both.

@@

## Case-study 2
### Methods
Here we used of space-based targets to generate a prioritisation to secure a representative sample of a species' intra-specific genetic variation. We used species occurrence and genomic data collected by the international IntraBioDiv project in the European Alps [@r451; see @r452 and @r478 for further explanation of data collection methods]. Although this dataset contains multiple plant species, we used data for the `r  cs2.params.LST[[MODE]]$common.name` (\textit{`r gsub('_', ' ',cs2.params.LST[[MODE]]$species.name,fixed=TRUE)`}). This species was chosen because it provides is locally wide-spread and has been shown to exhibit significant genetic structure [@r454]. Members of the IntraBioDiv project collected data using a $20^{\prime}$ longitude by $21^{\prime}$ latitude grid (approx. 22.3 km $\times$ 25 km; Figure 5a). They visited every second grid cell, and if the `r cs2.params.LST[[MODE]]$common.name` was detected in a cell, samples were collected from three individuals. Samples were genotyped using amplified fragment length polymorphisms [AFLP; @r453], and used to construct matrices denoting the presence/absence of polymorphisms at loci. In total, `r structurer::n.samples(cs2.spp.StructureData.LST[[1]])` individuals were genotyped at `r structurer::n.loci(cs2.spp.StructureData.LST[[1]])` markers.

>>>>

<!-- biodiversity processes are important -->
To fulfil the overarching aims of conservation, reserve networks must preserve both ecological and evolutionary processes [@r3; @r255]. Ecological processes, such as predator-prey interactions, pollination, and decomposition, are required for biodiversity to persist over short time-scales. Typically, they operate over small geographic domains--with exceptions such as migration and refugial habitats--and can be preserved using suitably large planning units [@r446] that each contain a discrete unit of habitat [@r448]. On the other hand, evolutionary processes are required for biodiversity to persist over long time-scales, and they typically operate over large geographic domains. Protected areas must preserve adaptive evolutionary processes to foster resilience against environmental change [eg. climate change; @r247]. Protected areas must also preserve neutral evolutionary processes [@r5; @r67; @r63]. These processes are associated with the breakdown of gene flow between populations. They are important for maintaining genetic diversity, and avoiding inbreeding depression. In recent decades, a wealth of data on biodiversity processes has become available to conservation planners [eg. bioclimatic, genetic, and trait data; @r33; @r453; @r460]. Yet this data is only rarely used to guide conservation planning [@r61]. This is due to that fact that existing reserve selection tools focus on preserving biodiversity patterns or processes--but not both.

@@

## Case-study 2
### Methods
Here we used of space-based targets to generate a prioritisation to secure a representative sample of a species' intra-specific genetic variation. We used species occurrence and genomic data collected by the international IntraBioDiv project in the European Alps [@r451; see @r452 and @r454 for further explanation of data collection methods]. Although this dataset contains multiple plant species, we used data for the `r  cs2.params.LST[[MODE]]$common.name` (\textit{`r gsub('_', ' ',cs2.params.LST[[MODE]]$species.name,fixed=TRUE)`}). This species was chosen because it provides is locally wide-spread and has been shown to exhibit significant genetic structure [@r454]. Members of the IntraBioDiv project collected data using a $20^{\prime}$ longitude by $21^{\prime}$ latitude grid (approx. 22.3 km $\times$ 25 km; Figure 5a). They visited every second grid cell, and if the `r cs2.params.LST[[MODE]]$common.name` was detected in a cell, samples were collected from three individuals. Samples were genotyped using amplified fragment length polymorphisms [AFLP; @r453], and used to construct matrices denoting the presence/absence of polymorphisms at loci. In total, `r structurer::n.samples(cs2.spp.StructureData.LST[[1]])` individuals were genotyped at `r structurer::n.loci(cs2.spp.StructureData.LST[[1]])` markers.
